---
title: "Text Analysis"
author: "Alexia"
date: "26/03/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#twitter_data


```{r, message = FALSE, echo=FALSE}
# Load the tidyverse packages
library(tidyverse)
twitter_data <- readRDS("ch_1_twitter_data.rds")

# Print twitter_data
twitter_data

# Print just the complaints in twitter_data
twitter_data %>% 
  filter(complaint_label == "Complaint")


# Start with the data frame
twitter_data %>% 
  # Group the data by whether or not the tweet is a complaint
  group_by(complaint_label) %>% 
  # Compute the mean, min, and max follower counts
  summarize(
    avg_followers = mean(usr_followers_count),
    min_followers = min(usr_followers_count),
    max_followers = max(usr_followers_count)
  )
```


#Counting user types

```{r, message=FALSE, echo=FALSE}

# Load the tidyverse package
library(tidyverse)

twitter_data %>% 
  # Filter for just the complaints
  filter(complaint_label == "Complaint") %>% 
  # Count the number of verified and non-verified users
  count(usr_verified)

```


#Summarizing user types


```{r,  echo=FALSE, message=FALSE}
twitter_data %>% 
  # Group by whether or not a user is verified
  group_by(usr_verified) %>% 
  summarize(
    # Compute the average number of followers
    avg_followers = mean(usr_followers_count),
    # Count the number of users in each category
    n = n()
  )


```

função unnest_tokens() pega a frase e conta palavra por palavra, primeiro argumento é "word"

```{r, message=FALSE, echo= FALSE}

# Load the tidyverse and tidytext packages
library(tidyverse)
library(tidytext)

tidy_twitter <- twitter_data %>% 
  # Tokenize the twitter data
  unnest_tokens(word, tweet_text) 

tidy_twitter %>% 
  # Compute word counts
  count(word) %>% 
  # Arrange the counts in descending order
  arrange(desc(n))
```

```{r, echo=FALSE, message=FALSE}

tidy_twitter <- twitter_data %>% 
  # Tokenize the twitter data
  unnest_tokens(word, tweet_text) %>% 
  # Remove stop words
  anti_join(stop_words)

tidy_twitter %>% 
  # Filter to keep complaints only
  filter(complaint_label == "Complaint") %>% 
  # Compute word counts and arrange in descending order
  count(word) %>% 
  arrange(desc(n))
```


#Visualizing complaints
a função coord_flip() muda a rotação do gráfico, o que pode facilitar a leitura das variáveis

```{r, message=FALSE, echo=FALSE}

word_counts <- tidy_twitter %>% 
  filter(complaint_label == "Complaint") %>% 
  count(word) %>% 
  # Keep words with count greater than 100
  filter(n > 100)

# Create a bar plot using word_counts with x = word
ggplot(word_counts, aes(x = word, y = n)) +
  geom_col() +
  # Flip the plot coordinates
  coord_flip()
```

#Visualizing non-complaints

```{r, message=FALSE, echo=FALSE}


word_counts <- tidy_twitter %>% 
  # Only keep the non-complaints
  filter(complaint_label == "Non-Complaint") %>% 
  count(word) %>% 
  filter(n > 150)

# Create a bar plot using the new word_counts
ggplot(word_counts, aes(x = word, y = n)) +
  geom_col() +
  coord_flip() +
  # Title the plot "Non-Complaint Word Counts"
  ggtitle("Non-Complaint Word Counts")
```


#A função tribble() cria um data frame do tipo tibble, onde as colunas são definidas por ~ e as entradas são separadas por vírgulas.

#A função bind_rows() junta linhas de dois dataframes. Um dos principais motivos para o uso de bind_rows sobre rbind é combinar dois quadros de dados com um número diferente de colunas. O rbind gera um erro nesse caso, enquanto o bind_rows atribui "NA" às linhas de colunas ausentes em um dos quadros de dados em que o valor não é fornecido pelos quadros de dados.

```{r, message=FALSE, echo=FALSE}

custom_stop_words <- tribble(
  # Column names should match stop_words
  ~word,  ~lexicon,
  # Add http, win, and t.co as custom stop words
  "http", "CUSTOM",
  "win",  "CUSTOM",
  "t.co", "CUSTOM"
)

# Bind the custom stop words to stop_words
stop_words2 <- stop_words %>% 
  bind_rows(custom_stop_words)

```

#Visualizing word counts using factors

A função fct_reorder() o primeiro argumento pega o que você quer modificar, e p segundo argumento pega  o vetor numérico que vc vai usar para reordernar os níveis.
```{r, message=FALSE, echo=FALSE}

word_counts <- tidy_twitter %>% 
  filter(complaint_label == "Non-Complaint") %>% 
  count(word) %>% 
  # Keep terms that occur more than 100 times
  filter(n > 100) %>% 
  # Reorder word as an ordered factor by word counts
  mutate(word2 = fct_reorder(word, n))

# Plot the new word column with type factor
ggplot(word_counts, aes(x = word2, y = n)) +
  geom_col() +
  coord_flip() +
  ggtitle("Non-Complaint Word Counts")
```

#Counting by product and reordering

```{r, echo=FALSE, message=FALSE}

word_counts <- tidy_twitter %>%
  # Count words by whether or not its a complaint
  count(word, complaint_label) %>%
  # Group by whether or not its a complaint
  group_by(complaint_label) %>%
  # Keep the top 20 words
  top_n(20, n) %>%
  # Ungroup before reordering word as a factor by the count
  ungroup() %>%
  mutate(word2 = fct_reorder(word, n))

```

#Visualizing word counts with facets

```{r, echo =FALSE, message=FALSE}

# Include a color aesthetic tied to whether or not its a complaint
ggplot(word_counts, aes(x = word2, y = n, fill = complaint_label)) +
  # Don't include the lengend for the column plot
  geom_col(show.legend = FALSE) +
  # Facet by whether or not its a complaint and make the y-axis free
  facet_wrap(~ complaint_label, scales = "free_y") +
  # Flip the coordinates and add a title: "Twitter Word Counts"
  coord_flip() +
  ggtitle("Twitter Word Counts")


```

###Creating a word cloud
```{r, message=FALSE, echo=FALSE}
# Load the wordcloud package
library(wordcloud)

# Compute word counts and assign to word_counts
word_counts <- tidy_twitter %>% 
  count(word)

wordcloud(
  # Assign the word column to words
  words = word_counts$word, 
  # Assign the count column to freq
  freq = word_counts$n, 
  max.words = 30
)

# Compute complaint word counts and assign to word_counts
word_counts <- tidy_twitter %>% 
  filter(complaint_label == "Complaint") %>% 
  count(word)

# Create a complaint word cloud of the top 50 terms, colored red
wordcloud(
  words = word_counts$word, 
  freq = word_counts$n, 
  max.words = 50,
  colors = "red"
)
```

